%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}

\name{Maxim Abramchuk} % Your name
\address{+375~29~530-0201 \\ maximabramchuck@gmail.com} % Your phone number and email
\address{Minsk, Belarus} % Your address

\begin{document}

%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Belarusian State University of Informatics and Radioelectronics, Minsk} \hfill {\em 2013-2017} \\ 
Faculty of Information Technologies and Control \\
B.S. in Computer Science \& Software Engineering \\

\end{rSection}

%----------------------------------------------------------------------------------------
%   TECHNOLOGY SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Have experience with}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Operating Systems     & Linux (Ubuntu, CentOS), Mac OS X \smallskip \\
Programming Languages & Ruby, Javascript (ES5, ES6), Coffescript, \\
                      & Haskell, Python, Typescript, Bash \smallskip \\
Frameworks            & Ruby on Rails, Angular, Ionic, Ember, Polymer \smallskip \\
Server technologies   & Nginx, Postfix \smallskip \\
Markup and Typesetting & HTML, Jade, Slim, CSS, SASS/SCSS, Less, Bootstrap, Stylus, JSX \smallskip \\
SQL Databases & PostgreSQL, MySQL, SQLite \smallskip \\
NoSQL Databases & MongoDB, Redis, Datomic \smallskip \\
Programming paradigms & Imperative, Object-oriented (class-based, prototype-based), \\
                      & Functional \smallskip \\
Tools                 & zsh, git, emacs, vim, tmux \smallskip \\
Other                 & ElasticSearch, Firebase, Cordova, Jquery, Lodash, Capistrano, \\
                      & NewRelic, Airbake, Rollbar, JenkinsCI, Redmine, Trello, Pivotal
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work positions}

\begin{rSubsection}{Rubyroid Labs, LLC}{April 2015- Present}{Full-stack Software Engineer}{Minsk, Belarus}
\item	Leaded a project and a team.
\item	Developed a couple of Ruby gems for communicating with mBaaS ecosystem.
\item Configured production server from scratch and setup automated Capistrano deployment for all the projects.
\item Implemented backend service for mobile apps.
\item Pursued the whole team to do TDD and code reviews. 
\item Worked on security-related features (IP whitelisting, XSS testing)
\item Automated code reviews using Rubocop and CircleCI, wrote an article to my blog about it.
\end{rSubsection}

\begin{rSubsection}{Datarockets, LLC}{June 2014 - April 2015}{Web Developer in Ruby department}{Minsk, Belarus}
\item Participated in all stages of design and development on many projects.
\item	Leaded a small team.
\item	Optimized some perfomance issues.
\item Made fully-automated production server setup
\item Did code reviews.
\item Did a legacy project code refactoring.
\item	Did requirements gathering, directly communicated with clients.
\item	Planned some projects, sprints, created roadmaps.
\item	Developed some internal gems.
\item	Leaded the internal movement to open source some of the internal gems.
\item	Documented systems and infrastructure by creating textual and visual documents, as well as screencasts.
\item Presented multiple times at the department meetings.
\item	Taught Junior developers.
\item	Maintained the Twitter account and team site.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%   NOTES SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Social activities}

\begin{rSubsection}{Belarus Ruby User Group}{June 2015}{Speaker}{Minsk, Belarus}
  \item	Talked about our experience using gem 'cells' and other parts of Trailblazer (new architecture for Rails) framework. Video from the talk is available at my YouTube channel.
\end{rSubsection}

\begin{rSubsection}{WrocLove.rb conference}{April 2015}{Speaker}{Wroclaw, Poland}
  \item	Talked about new way of designing Rails views, gem 'cells' from Trailblazer framework. Video from the talk is available at my YouTube channel.
\end{rSubsection}

\begin{rSubsection}{Codementor.com}{June 2015 - Present}{Mentor, Problem Solver}{Minsk, Belarus}
  \item	Teach people how to code. Solve different problems and fix the issues. Have more then 30 successful sessions.
\end{rSubsection}

\begin{rSubsection}{Meduim.com}{May 2015 - Present}{Blogger}{Minsk, Belarus}
  \item	Write mostly about programming, technologies, tech conferences and travelling.
\end{rSubsection}

\end{rSection}

% ----------------------------------------------------------------------------------------
%  LINKS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Links}

\item \href{https://github.com/maximabramchuck}{Github - https://github.com/maximabramchuck}
\item \href{https://www.linkedin.com/pub/maxim-abramchuck/a0/5bb/994}{LinkedIn - https://www.linkedin.com/pub/maxim-abramchuck/a0/5bb/994}
\item \href{https://medium.com/@MaximAbramchuk}{Medium - https://medium.com/@MaximAbramchuk}
\item \href{https://www.youtube.com/channel/UClJ7ss6npGtPTKw8PtXeIww/videos}{Youtube channel- https://www.youtube.com/channel/UClJ7ss6npGtPTKw8PtXeIww/videos}
\item \href{https://www.codementor.io/maximabramchuck}{Codementor - https://www.codementor.io/maximabramchuck}


\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
